Notes on Control Plane Inference

### 2021-05-27 inference.tex
prove disjoint commutativity

@@

  \item[$(b = e_1 = e_2)$] Since $y \not \in\bfvs(e_1 = e_2) = \efvs(e_1) \cup
    \efvs(e_2)$, $y \not \in \bfvs(e_i)$ for $i =1,2$. Compute as follows:
    \[\begin{array}{ll}
    \pkt\{y \mapsto v_1\} \models e_1 = e_2
    \iff \edenote{e_1}\pkt\{y \mapsto v_1\} = \edenote{e_2}\pkt\{y \mapsto v_1\} \\
    \iff\edenote{e_1}\pkt\{y \mapsto v_2\} = \edenote{e_2}\pkt\{y \mapsto v_2\} & \text{by Lemma~\ref{lem:exp-param-noninter}} \\
    \iff \pkt\{y\mapsto v_2\} \models e_1 = e_2
    \end{array}
    \]
  \end{enumerate}
\end{proof}

@@

\begin{lemma}[Disjoint Commutativity]
  \label{lem:disj-comm}
  For $c_1,c_2 \in \Cmd$, and $\sigma \in \State$ if $\fvs(c_1) \cap
  \fvs(c_2) = \emptyset$, $ \forall \pkt \in \Pkt. \denote{c_1;c_2}^\sigma\pkt =
  \denote{c_2;c_1}^\sigma \pkt$.
\end{lemma}
\begin{proof}
  \todo[inline]{todo}
\end{proof}

>>>>

\begin{lemma}[Set Pseudo-Parametricity]
  \label{lem:parametricity-set}
  For $c \in \Cmd$, $\sigma : \State$, $y \in \Var$, $\pkt \in \Pkt$, if $Y
  \subseteq \Var \setminus \fvs(c)$, then $\forall \pkt' \in \denote{c}^\sigma
  \pkt$, $\pkt'(y) = \pkt(y)$.
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:parametricity}.
\end{proof}

@@

  \item[$(b = e_1 = e_2)$] Since $y \not \in\bfvs(e_1 = e_2) = \efvs(e_1) \cup
    \efvs(e_2)$, $y \not \in \bfvs(e_i)$ for $i =1,2$. Compute as follows:
    \[\begin{array}{ll}
    \pkt\{y \mapsto v_1\} \models e_1 = e_2 \\
    \iff \edenote{e_1}\pkt\{y \mapsto v_1\} = \edenote{e_2}\pkt\{y \mapsto v_1\} \\
    \iff\edenote{e_1}\pkt\{y \mapsto v_2\} = \edenote{e_2}\pkt\{y \mapsto v_2\} & \text{by Lemma~\ref{lem:exp-param-noninter}} \\
    \iff \pkt\{y\mapsto v_2\} \models e_1 = e_2
    \end{array}
    \]
  \end{enumerate}
\end{proof}

@@

\begin{lemma}[Unused Variable Set Noninterference]
  \label{lem:param-noninter-set}
  For $c \in \Cmd$, $\sigma : \State$, $\pkt \in \Pkt$,
  $\{v_1,v_2\} \subseteq \Value$, $Y \subseteq \Var \setminus \fvs(c)$,
  $\denote{c}^\sigma \pkt\{y \mapsto v\} =_{\Var \setminus Y}\denote{c}^\sigma\pkt\{y \mapsto v\}$.
\end{lemma}

\begin{proof}
  By Lemma~\ref{lem:param-noninter}.
\end{proof}

\begin{lemma}[Disjoint Commutativity]
  \label{lem:disj-comm}
  For $c_1,c_2 \in \Cmd$, and $\sigma \in \State$ if $\fvs(c_1) \cap
  \fvs(c_2) = \emptyset$, $ \forall \pkt \in \Pkt. \denote{c_1;c_2}^\sigma\pkt =
  \denote{c_2;c_1}^\sigma \pkt$.
\end{lemma}
\begin{proof}
  Let $c_1, c_2$, $\sigma$, and $\pkt$ be given as above.
  Let $\{i,j\} = \{1,2\}$. Observe:
  \[\begin{array}{ll}
  \denote{c_i;c_j}^\sigma \pkt
  = {\denote{c_j}\sigma}^\dagger\left(\denote{c_i}^\sigma \pkt\right)
  \end{array}\]

  Let $V = \Var \setminus \fvs(c_1;c_2)$. Let $P_1 = \denote{c_1}^\sigma \pkt$,
  and $P_2 = \denote{c_2}^\sigma \pkt$. By Lemma~\ref{lem:parametricity-set}, the following hold
  \[P_1 =_{\fvs(c_2) \cup V} \{\pkt\}\] \[P_2 =_{\fvs(c_1) \cup V} \{\pkt\}\]
  So, Let $P_{12} = {\denote{c_2}^\sigma}^\dagger P_1$, and $P_{21} =
  {\denote{c_1}^\sigma}^\dagger P_2$. Again, by
  Lemma~\ref{lem:parametricity-set}, the following equivalences hold
  \[P_{12} =_{\fvs(c_1) \cup V} P_1\] \[P_{21} =_{\fvs(c_2) \cup V} P_2\]
  Now by Lemma~\ref{lem:proj-set-subset}, we know $P_{12} =_V \{\pkt\} = P_{21}$.

  Now by Lemma~\ref{lem:param-noninter-set} we know
  \[P_{21} =_{\fvs(c_1)} P_1\] \[P_{12} = \fvs(c_2) P_2\]

  Then Lemma~\ref{lem:proj-set-subset} gives
  \[P_{12} =_{\fvs(c_1)} {P_1}\] \[P_{21} =_{\fvs(c_2)} {P_2}\]

  Finally Lemma~\ref{lem:union} proves our goal:
  \[P_{12} =_{\fvs(c_1) \cup \fvs(c_2) \cup V} P_{21}\]
